ExpressionView - an interactive viewer for biclusters identified in gene expression data

### 2010-01-11 expressionviewnote/expressionview.tex
ExpressionView note: Updated screenshot.
Updated ExpressionView application note author list.

\usepackage[pdftex,colorlinks,bookmarks=false,citecolor=blue,linkcolor=red,urlcolor=blue]{hyperref}
\newcommand{\thefirstpage}{1} \newcommand{\thelastpage}{1}

@@

\firstpage{1}
\application{}
\title[ExpressionView]{ExpressionView - an interactive viewer for biclusters identified in gene expression data}
\author[Andreas L\"uscher, G\'abor Cs\'ardi, Aitana Morton de Lachapelle, Zolt\'an Kutalik, and Sven Bergmann]{Andreas L\"uscher$^1$, G\'abor Cs\'ardi$^{1,2}$, Aitana Morton de Lachapelle$^{1,2}$, Zolt\'an Kutalik$^{1,2}$, and Sven Bergmann$^{1,2}$\footnote{to whom correspondence should be addressed}}
\address{
	$^{1}$Swiss Institute of Bioinformatics, Lausanne, Switzerland\\
	$^{2}$Department of Medical Genetics, University of Lausanne, Lausanne, Switzerland
}

@@

\bibitem[Cs{\'a}rdi et~al.(2009)]{csardi09}
Cs{\'a}rdi,G., Kutalik,Z. and Bergmann,S. (2009)
Eisa.
\href{http://dx.doi.org/}{\emph{Bioinformatics}, ...}

>>>>

\usepackage[dvipdfm,colorlinks,bookmarks=false,citecolor=blue,linkcolor=red,urlcolor=blue]{hyperref}
\newcommand{\thefirstpage}{1} \newcommand{\thelastpage}{1}

@@

\firstpage{1}
\application{}
\title[ExpressionView]{ExpressionView - an interactive viewer for biclusters identified in gene expression data}
\author[Andreas L\"uscher, G\'abor Cs\'ardi, Aitana Morton de Lachapelle, Zolt\'an Kutalik, and Sven Bergmann]{Andreas L\"uscher$^1$, G\'abor Cs\'ardi$^{1,2}$, Aitana Morton de Lachapelle$^{1,2}$, Zolt\'an Kutalik$^{1,2}$, Bastian Peter$^{1,2}$ and Sven Bergmann$^{1,2}$\footnote{to whom correspondence should be addressed}}
\address{
	$^{1}$Swiss Institute of Bioinformatics, Lausanne, Switzerland\\
	$^{2}$Department of Medical Genetics, University of Lausanne, Lausanne, Switzerland
}

@@

\bibitem[Cs{\'a}rdi et~al.(2009)]{csardi09}
Cs{\'a}rdi,G., Kutalik,Z. and Bergmann,S. (2009)
Modular analysis of gene expression data with R.
\href{http://dx.doi.org/}{\emph{Bioinformatics}, ...}
